preparation

### 2025-03-31 d2mr_manuscript.qmd
Updating document names to reflect full sample data

One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

>>>>

One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis. This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing]. Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed. If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis]. Thus, I pose my final hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own. Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

### 2025-03-31 data/preparation.Rmd
Added informative comment
Updating document names to reflect full sample data

---
title: "preparation"
author: "Reilly Amera"
date: "2025-02-26"
output: html_document
---

```{r setup}
library(tidyverse)
```

```{r read-in}
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
```

```{r cleaning}
# removing unnecessary columns
child <- child %>% 
  select(-c(1:5, 8:18))
child <- child[-c(1, 2),]

parent <- parent %>% 
  select(-c(1:6, 8:18))
parent <- parent[-c(1, 2),]

# replacing one NA (participant forgot ID)
child$PID[is.na(child$PID)] <- 1

# renaming 'finished' columns 
child <- child %>% 
  rename(Cfinished = Finished)

parent <- parent %>% 
  rename(Pfinished = Finished)
```

```{r wrangling}
# merging datasets
youtube <- full_join(parent, child, by = "PID")

# removing instances where either parents or children failed to finish
youtube <- youtube %>% 
  filter(Pfinished == Cfinished)
```

>>>>

---
title: "preparation"
author: "Reilly Amera"
date: "2025-03-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup}
library(tidyverse)

# Read in data
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
```

```{r cleaning}
# Remove rows that do not contain survey data
parent <- parent[-c(1, 2),]
child <- child[-c(1, 2),]
```

```{r parent cleaning}
# Parent cleaning
parent <- parent %>% 
  # self consent = agree
  filter(Pconsent_self == "Agree") %>% 
  # child consent = agree
  filter(`Pconsent-child` == "Agree") %>% 
  # remove duplicates
  mutate(Q_RelevantIDDuplicate = 
           # Logical operators
           ifelse(is.na(Q_RelevantIDDuplicate), FALSE, TRUE)) %>% 
  filter(Q_RelevantIDDuplicate != TRUE) %>% 
  # filter attn checks
  filter(yt_opinions_4 == "A lot") %>% 
  # get rid of unnecessary columns
  select(-c(StartDate:Q_RelevantIDLastStartDate))
```

```{r parent wrangling}
# Parent reported child age
parent <- parent %>% 
  # Create one birthday column
  unite(bday, `bday#1_1`, `bday#2_1`, sep = " ", remove = FALSE) %>% 
  unite(bday, bday, `bday#3_1`, sep = ", ", remove = FALSE) %>% 
  # Parse birthdays as dates
  mutate(bday = mdy(bday)) %>% 
  # Age column
  mutate(P_age = time_length(interval(bday, Sys.Date()), "years") %>% floor())
```

```{r child cleaning}
child <- child %>% 
  # remove survey testing responses 
  filter(!is.na(transaction_id)) %>% 
  # consent = agree
  filter(Cconsent == "YES") %>% 
  # get rid of unnecessary columns
  select(-c(StartDate:UserLanguage)) %>% 
  # gc = 1 - embedded data; good/complete responses
  filter(gc == 1)
```

```{r merge}
# Merging data
youtube <- inner_join(parent, child, by = join_by(transaction_id))
```

```{r age wrangling}
youtube <- youtube %>% 
  # Do child ages match parent ages?
  mutate(age_match = ifelse(
    P_age == age,
    TRUE,
    FALSE
  ))

# age discrepancies
false_age <- youtube %>% 
  select(age_match, bday, P_age, age, transaction_id) %>% 
  filter(age_match == FALSE) %>% 
  mutate(age = as.numeric(age)) %>% 
  mutate(difference = abs(P_age - age)) %>% 
  mutate(large_diff = ifelse(
    difference > 1,
    TRUE,
    FALSE
  )) %>% 
  filter(large_diff == TRUE) %>% 
  select(transaction_id)

# write_csv(false_age, "transaction_ids.csv")
```

```{r youtube wrangling}
# Time Scores
```

```{r youtube composites}
### Recoding factor variables as numeric variables to create aggregate scores
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
                     "Really disagree" = 1,
                     "Disagree" = 2,
                     "I don't know" = 3,
                     "Agree" = 4,
                     "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
           ~ recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  mutate(
    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ recode(.,
                    "Really disagree" = 1,
                    "Disagree" = 2,
                    "Neither agree nor disagree" = 3,
                    "Agree" = 4,
                    "Really agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))

### Composite scores
# Racial attitudes score -- total possible score = 20
youtube <- youtube %>% 
  mutate(malleable_score = rowSums(across(malleable_1:malleable_4))) %>% 
  mutate(malleable_score = malleable_score/20)

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 20
  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
  # homophily-behave -- total possible score = 20
  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
  # parasocial -- total possible score = 20
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/20) %>%
  mutate(h_behave_score = h_behave_score/20) %>%
  mutate(parasocial_score = parasocial_score/20) %>%
  mutate(composite = composite/60)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
  mutate(regularity_score = regularity_score/35)
```

```{r}
# H1: time spent on YouTube and children’s observation of racial regularities covary
```

```{r}
# H2: if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups
```

```{r}
# H3: the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities
```

```{r}
# H4: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own
```
